\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{bold-extra}

\usepackage[hidelinks]{hyperref}

\input{glyphtounicode}

%----------FONT OPTIONS----------
% \usepackage[sfdefault]{FiraSans}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-68pt}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.35004pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
\hypersetup{
    pdftitle={HuyLaiResume},
    pdfsubject={Huy Lai Resume},
    pdfauthor={Huy Lai}
}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Date (and GPA) are placed inline on the heading line rather than in a
% right-aligned tabular cell. Geometry-based extractors (markitdown/pdfminer)
% column-group anything at the right margin and emit it out of order; keeping
% the date in the normal left-to-right text flow makes it extract in sequence.
\newcommand{\resumeDegreeheading}[5]{
  \vspace{-2pt}\item
    \textbf{#1} $\vert$ #2 $\vert$ {\small #3} $\vert$ {\small GPA: #5 / 4.000}\par\nobreak
    {\small #4}\par\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \textbf{#1} $\vert$ #2 ; \textit{#3} $\vert$ \textit{#4}\par\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    {\small #1 $\vert$ #2}\par\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=10pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Huy Lai} \\ \vspace{1pt}
    \small{US Citizen} \\
    \small{Austin, Texas, United States of America} \\
    \small \href{mailto:lai.huy.075@gmail.com}{\underline{lai.huy.075@gmail.com}} $\vert$
    \href{https://www.linkedin.com/in/huy-lai-93a2b4211/}{\underline{linkedin.com/in/huy-lai-93a2b4211/}} $\vert$
    \href{https://lai-huy.github.io}{\underline{lai-huy.github.io}}
\end{center}

%-----------PROGRAMMING SKILLS-----------
% START GENAI
\vspace{-14pt}
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages}: Java, Python, C/C++, Ruby, SQL, JavaScript, TypeScript, HTML, CSS \\ \vspace{2pt}
        \textbf{Frameworks \& Libraries}: Spring Boot, React.js, Next.js, Node.js, Ruby on Rails, JUnit, Mockito, PyTorch, TensorFlow, Scikit-Learn \\ \vspace{2pt}
        \textbf{Data \& Messaging}: Apache Kafka, OpenSearch, Elasticsearch, PostgreSQL, Oracle, H2, AWS S3, Jackson \\ \vspace{2pt}
        \textbf{DevOps \& Tools}: Git, Docker, Maven, AWS, GCP, Nginx, Prometheus, Kibana, Firebase, Pub/Sub, VS Code, IntelliJ
    }}
\end{itemize}
% END GENAI

%-----------EXPERIENCE-----------
\vspace{-10pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{\href{https://usa.visa.com/}{\underline{Visa Inc.}}}
      {Austin, TX}{Aug 2025 --- Present}
      \resumeItemListStart
        \resumeItem{Engineered a Kafka MCP Server to automate resource provisioning via Jira, GitHub, and Wiki integration, reducing developer onboarding time from weeks to days.}
        \resumeItem{Built an indexing library in Java with resilient OpenSearch/In-Memory storage and byte-level S3 range optimization for sub-100ms audit log lookups.}
        \resumeItem{Enhanced user experience by optimizing UI performance and implementing clean, maintainable APIs across e-commerce applications.}
        \resumeItem{Diagnosed and escalated critical bugs, enhancing system reliability and browser compatibility.}
    \resumeItemListEnd

    % \vspace{-10pt}
    \resumeSubheading
      {Software Engineer}{\href{https://www.totalcare2u.com/}{\underline{Total Care 2U}}}
      {Waxahachie, TX}{Jul 2024 --- Jul 2025}
      \resumeItemListStart
        \resumeItem{Automated the end-to-end ETL (Extract, Transform, Load) process for migrating patient medical data into an advanced Electronic Health Record (EHR) system.}
        \resumeItem{Validated patients' personal information for accuracy and completeness to ensure data integrity.}
        \resumeItem{Designed automated quality assurance procedures to verify data consistency across systems.}
        \resumeItem{Presented progress demos to cross-functional teams to ensure stakeholder alignment and gather feedback.}
    \resumeItemListEnd

    % \vspace{-10pt}
    \resumeSubheading
      {Product Owner and Developer}{\href{https://www.bvcog.org/}{\underline{BVCOG}}}
      {Bryan, TX}{Aug 2023 --- Dec 2023}
      \resumeItemListStart
        \resumeItem{Spearheaded the development of a scalable full-stack application using Ruby on Rails, capable of managing over 400 contracts simultaneously.}
        \resumeItem{Implemented and rigorously tested 85+ individual features using Cucumber and RSpec to ensure high-quality code delivery}
        \resumeItem{Facilitated requirement gathering as primary liaison between developers and stakeholders, driving iterative feedback loops.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\vspace{-10pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeDegreeheading
      {Texas A\&M University}{College Station, TX}
      {May 2025}{Master of Computer Science}
      {3.700}
  
    \resumeDegreeheading
      {Texas A\&M University}{College Station, TX}
      {May 2024}{Bachelor of Science in Computer Science, cum laude, Minors: Cybersecurity, Mathematics}
      {3.594}
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\vspace{-5pt}
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{Improving CLIP Training} $\vert$ \emph{torch, Self-Supervised Learning, Contrastive Learning}}{Aug 2024 --- Dec 2024}
        \resumeItemListStart
            \resumeItem{Optimized bimodal contrastive SSL models using global contrastive loss for scalable image-text learning.}
            \resumeItem{Implemented SogCLR/iSogCLR, enhancing retrieval accuracy and zero-shot classification.}
            \resumeItem{Analyzed optimizers and loss functions to improve model convergence and multimodal generalization.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\textbf{ScriptSearch} $\vert$ \emph{Python, Cloud Functions, Firebase, Pub/Sub, Typesense}}{Jan 2024 --- May 2024}
        \resumeItemListStart
            \resumeItem{Built a transcript-based YouTube search engine with fast, keyword-driven results and timestamped links.}
            \resumeItem{Engineered a scalable scraping pipeline using Golang, Pub/Sub, and Firebase Functions.}
            \resumeItem{Achieved sub-4s average query time across 250+ videos using Typesense indexing.}
            \resumeItem{Delivered a full-stack app in 15 weeks through Agile development and user-driven design.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
